Detecting Facial Expressions in Video Stills from Professional Tennis Matches

### 2017-12-12 paper/paper.Rmd
editing system time section

Figure \@ref(fig:timeFigure) displays the processing time required by the APIs for each image.

@@

```{r timeFigure, fig.cap="System time taken by the four APIs to finish searching individual images, by number of faces discovered. Skybiometry is the fastest, and Microsoft is the slowest. When there are few faces found there is more variable time taken per image.\\label{fig:timeFigure}"}
# 
# t1 <- ggplot(times) +  
#   geom_smooth(aes(x=n, y=time.sys.self, colour=type), method="lm") + 
#   xlab("Number of faces detected") + ylab("System time (sec)") +  
#   scale_colour_manual("API", values=type.colours) + theme(legend.position = "none")

@@

# letter value plots
t2 <- ggplot(times, aes(as.factor(n), time.sys.self)) + 
  geom_lv(aes(fill = ..LV..)) +
  ylim(c(0, 0.1)) + 
  facet_wrap(~type) +
  xlab("Number of faces detected")

@@

```{r accessories, eval=FALSE, fig.cap = "\\label{tab:accessories}"}
aminFaces %>%
  filter(type=="Manual") -> ManFaces

>>>>

Figure \@ref(fig:timeFigure) displays the processing time required by the APIs for each image, as a letter value plot (*** add in reference to Heik'e paper). A letter value plot is like a boxplot, but more suited to skewed data like this. (Both Microsoft and Google have a few eimages each where they have taken a long time to complete and these were removed from this plot.) The times are quite variable between APIs, with Skybiometry being the most consistently fast. Microsoft and Animetrics are quite variable regardless of the number of faces found. Google is variable in time taken when there are few faces present, and then takes a little longer on average to find faces as the number of them in the image increases.

@@

```{r timeFigure, fig.height=6, fig.cap="System time taken by the four APIs to finish searching individual images, by number of faces discovered, displayed as a letter value plot.  Skybiometry is the most consistently fast.\\label{fig:timeFigure}"}
# 
# t1 <- ggplot(times) +  
#   geom_smooth(aes(x=n, y=time.sys.self, colour=type), method="lm") + 
#   xlab("Number of faces detected") + ylab("System time (sec)") +  
#   scale_colour_manual("API", values=type.colours) + theme(legend.position = "none")

@@

# letter value plots
t2 <- ggplot(times, aes(as.factor(n), time.sys.self)) + 
  geom_lv(aes(fill = ..LV..)) +
  #ylim(c(0, 0.1)) + 
  facet_wrap(~type) +
  scale_y_continuous("System time (ms)", 
    breaks=seq(0, .08, .02), limits=c(0, 0.08)) +
  # somethings funky when try to change axis labels
  xlab("Number of faces detected")

@@

```{r accessories, eval=TRUE, fig.cap = "\\label{tab:accessories}"}
aminFaces %>%
  filter(type=="Manual") -> ManFaces
